Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.

### 2015-05-25 papers/data_paper/datapaper.tex
thu
ale?

\shorttitle{Data paper}
\shortauthors{Savorgnan et al.}

@@

\title{Data paper}

\author{G. A. D. Savorgnan\altaffilmark{1} and A. W. Graham\altaffilmark{1}}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}

@@

in the local Universe {\bf (Graham, Dullo, Savorgnan 2015)}.

@@

% \onecolumngrid
% \subsection{individual galaxies}
% \label{sec:indgal}
%
% individual galaxies \\
%
% \clearpage\newpage\noindent
% {\bf IC 1459 \\}
%
% IC 1459 is an elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
% nuclear dust and an indication of a central stellar disk \citep{forbes1994ic1459}.
% The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
% This galaxy has also a partially depleted core ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
%
% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + Gaussian-AGN model ($R_{\rm e} = 61''.1$, $n=6$).
% %\cite{lasker2014data} used a S\'ersic-bulge + mask-core model ($R_{\rm e} = 62''.4$, $n=8.25$).
% %\cite{rusli2013} adopted a core-S\'ersic model ($R_{\rm e} = 45''.43$, $n=7.6$).
%
% \emph{1D fit -- }
% Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
% We masked the innermost $6''.1$ affected by the partially depleted core 
% and we fit this galaxy with a S\'ersic profile. 
%
% \emph{Other models -- } 
%
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for IC 1459.}
% \end{center}
% \end{figure}
%
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for IC 1459.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
% T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
% T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
% \hline
% S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
% R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
% L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:ic1459}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf IC 2560 \\}
%
% IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
% and dust within the central $2''.5$ \citep{martini2003}.
%
% %\cite{sani2011} used a S\'ersic-bulge + exponential-disk + Gaussian-AGN model ($R_{\rm e} = 27''.5$, $n=2$).
%
% \emph{1D fit -- }
% A visual inspection of the image of IC 2560 reveals a boxy bulge and
% a large scale bar that extends out to $R \lesssim 43''$.
% The disk appears to be slightly lopsided along the direction of the bar,
% due to two non-symmetric ansae, but it becomes symmetric beyond $R \gtrsim 60''$. 
% This is why the surface brightness profile deviates from a perfect exponential
% in the radial range $42'' \lesssim R \lesssim 60''$, which has been excluded from the fit.
% Motivated by the presence of a strong optical AGN and dust in the nucleus, 
% we accounted for an excess of non-stellar light by adding a central Gaussian component to the model.
% %Our final 1D model consists of a S\'ersic-bulge + exponential-disk + Ferrer-bar + Gaussian-AGN.
% %Similarly, our 2D model consists of a S\'ersic-bulge + exponential-disk + Gaussian-bar + Gaussian-AGN.\\
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for IC 2560.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for IC 2560.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $6.1$  &  $0.8$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.5$  &  $0.6$ \\
% %T.W. 2D	&  &  & \\
% \hline
% S+11         & S-bul + e-d + G-n & $27.5$  &  $2.0$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:ic2560}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf IC 4296 \\}
%
% IC 4296 is an elliptical galaxy. % with a radio jet \citep{liuxie1992}.
% Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
%
% %\cite{sani2011} fit this galaxy with a S\'ersic-bulge + Gaussian-AGN model ($R_{\rm e} = 33''.6$, $n = 4$).
% %\cite{lasker2014data} employed a S\'ersic-bulge + mask-core model ($R_{\rm e} = 97''.8$, $n=8.2$).
%
% \emph{1D fit -- }
% After masking the innermost $6''.1$, % affected by the (unresolved) partially depleted core,
% we found that a single S\'ersic profile provides a fairly good description of this galaxy.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for IC 4296.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for IC 4296.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
% T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
% T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
% \hline
% S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
% L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:ic4296}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M31 -- NGC 0224 \\}
%
% M31, the Andromeda galaxy, is a spiral galaxy. 
% Although for decades this galaxy had been classified as an unbarred spiral,
% recent works have unraveled the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}.
% M31 also features a pseudo-ring-like structure at $R \sim 50'$ \citep{athanassoulabeaton2006m31}. 
%
%
% \emph{1D fit -- }
% We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
% The region $2000'' \lesssim R \lesssim 3400''$, where the pseudo-ring is observed, was excluded from the fit.
% A S\'ersic + exponential fit is clearly not adequate to describe the light profile of M31.
% The residuals of such fit display a structure in correspondence of the bar ($R \lesssim 1500''$).
% The bar was thus fit with a Ferrer function.
%
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M31.}
% \end{center}
% \end{figure}
%
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M31.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + e-d + F-bar & $418.6$  &  $2.2$ \\
% T.W. 1D eq.  & S-bul + e-d + F-bar & $173.6$  &  $1.3$ \\
% %T.W. 2D	& $$  & $$  &  $$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m31}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M49 -- NGC 4472 \\}
%
% M49, the brightest member of the Virgo cluster, is a giant elliptical galaxy 
% with a partially depleted core ($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
% %M49 is a slow-rotator \citep{atlas3dIII-MNRAS}.
%
% %\cite{ferrarese2006acsvcs} modeled this galaxy with a core-S\'ersic profile ($R_{\rm e} = 208''$, $n = 5.5$).
% %Also \cite{rusli2013} used a core-S\'ersic model ($R_{\rm e} = 199''$, $n = 5.6$).
%
% \emph{1D fit -- }
% We excluded from the fit the innermost $12''$.
% We found no evidence for embedded components and
% we fit M49 with a single S\'ersic profile.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M49.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M49.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c & $190.2$  &  $6.6$ \\
% T.W. 1D eq.  & S-bul + m-c & $135.3$  &  $5.4$ \\
% T.W. 2D      & S-bul + m-c & $151.9$  &  $5.5$ \\
% \hline
% R+13         & core-S\'ersic & $199.0$  &  $5.6$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m49}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M59 -- NGC 4621 \\}
%
% M59 is an elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
% and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}.
% %M59 is a fast-rotator \citep{atlas3dIII-MNRAS}.
%
% %\cite{sani2011} modeled this galaxy with a single S\'ersic-bulge model ($R_{\rm e} = 70''.1$, $n = 5$).
% %\cite{vika2012} used a S\'ersic-bulge + mask-core model ($R_{\rm e} = 54''.7$, $n = 5.7$). 
%
% \emph{1D fit -- }
% The intermediate-scale embedded disk is clearly visible in our unsharp mask image, and 
% the velocity field confirms the presence of a rapidly rotating component. 
% Although faint, it is important to account for the presence of this disk.
% A single S\'ersic fit produces bad residuals.
% The fit notably improves if an embedded exponential disk function 
% is added to the final model.
% We chose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.
%
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
% \caption{Best-fit model and isophotal parameters for M59.}
% \end{center}
% \end{figure}
%
% \begin{table}[h]
% \small
% \caption{Best-fit parameters for M59.}
% \begin{center}
% \begin{tabular}{llcc}
% \hline
% {\bf Work} & {\bf Model}   & $\bm R_{\rm e}$    & $\bm n$ \\
%   &  &  $[\rm arcsec]$ & \\
% \hline
% T.W. 1D maj. & S-bul + m-c + e-id & $48.0$  &  $5.5$ \\
% T.W. 1D eq.  & S-bul + m-c + e-id & $90.9$  &  $8.8$ \\
% %T.W. 2D	&    & $$  &  $$ \\
% \hline 
% S+11         & S-bul       & $70.1$  &  $5.0$ \\
% V+12         & S-bul + m-c & $54.7$  &  $5.7$ \\
% \hline
% \end{tabular}
% \end{center}
% \label{tab:m59}
% \end{table}
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
%
% {\bf M60 -- NGC 4649 \\}
%
% exclude it, doesn't make sense
%
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \clearpage\newpage\noindent
% {\bf M64 -- NGC 4826 \\}
%
% M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. 
%
% %B12 model the galaxy image with a 2D S\'ersic function + exponential disk ($n = 1.49$). \\
% \emph{1D fit -- }
% A large-scale bar ($R \lesssim 50''$) can be identified in the unsharp mask 
% and produces corresponding peaks in the ellipticity, PA and B4 profiles.
% We modeled it with a Ferrer function.
% Additional peaks in the ellipticity, PA and B4 profiles at $R \sim 15''$ 
% signal the presence of an embedded disky component, that we described with a low-$n$
% S\'ersic function.

>>>>

\shorttitle{True-to-life galaxy decomposition}
\shortauthors{Savorgnan \& Graham}

@@

\title{Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.}

\author{G. A. D. Savorgnan and A. W. Graham}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}

@@

in the local Universe \citep{GDS2015}.

@@

  \onecolumngrid
  \subsection{individual galaxies}
  \label{sec:indgal}

  individual galaxies \\

  \clearpage\newpage\noindent
  {\bf IC 1459 \\}

  IC 1459 is an elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
  nuclear dust and an indication of a central stellar disk \citep{forbes1994ic1459}.
  The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
  This galaxy has also an unresolved partially depleted core \citep{rusli2013}. \\ % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).

  \emph{1D fit -- }
  Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
  We masked the innermost $6''.1$ affected by the partially depleted core 
  and we fit this galaxy with a S\'ersic profile. \\

  \emph{Other models -- } 
  The best-fit model of L+14 is in reasonable agreement with our results. 
  S+11 obtained the smallest S\'ersic index because they fit a nuclear component rather than masking the core. 
  R+13 obtained the smallest effective radius 
  because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for IC 1459.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 1459.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
  T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
  T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
  \hline
  S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
  R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
  L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic1459}
  \end{table}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \clearpage\newpage\noindent
  {\bf IC 2560 \\}

  IC 2560 is a barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
  and dust within the central $2''.5$ \citep{martini2003}.\\

  \emph{1D fit -- }
  A visual inspection of the image of IC 2560 reveals a boxy bulge and
  a large scale bar that extends out to $R_{\rm maj} \lesssim 43''$.
  The disk appears to be slightly lopsided along the direction of the bar,
  due to two non-symmetric ansae, but it becomes symmetric beyond $R_{\rm maj} \gtrsim 60''$. 
  This is why the surface brightness profile deviates from a perfect exponential
  in the radial range $42'' \lesssim R_{\rm maj} \lesssim 60''$, which has been excluded from the fit.
  Motivated by the presence of a strong optical AGN and dust in the nucleus, 
  we accounted for an excess of non-stellar light by adding a central Gaussian component to the model.\\

  \emph{Other models -- } 
  In their model, S+11 did not account for the bar component and thus overestimated the effective radius and the S\'ersic index of the bulge.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for IC 2560.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 2560.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-bar + G-n & $6.1$  &  $0.8$ \\
  T.W. 1D eq.  & S-bul + e-d + F-bar + G-n & $4.5$  &  $0.6$ \\
  \hline
  S+11         & S-bul + e-d + G-n & $27.5$  &  $2.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic2560}
  \end{table}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \clearpage\newpage\noindent
  {\bf IC 4296 \\}

  IC 4296 is an elliptical galaxy. 
  Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core.

  \emph{1D fit -- }
  After masking the innermost $6''.1$, 
  we found that a single S\'ersic profile provides a fairly good description of this galaxy.

  \emph{Other models -- } 
  S+11 obtained the smallest effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
  L+14 obtained the largest effective radius and S\'ersic index, 
  although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R > 100''$), 
  implying the need for a smaller $R_{\rm e}$ and $n$. 
  We did not find any conclusing explanation for this, 
  but we suspect it may be due to the different pixel weighting scheme that they used.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for IC 4296.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 4296.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
  T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
  T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
  \hline
  S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
  L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic4296}
  \end{table}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \clearpage\newpage\noindent
  {\bf M31 -- NGC 0224 \\}

  M31, the Andromeda galaxy, is a spiral galaxy. 
  Although for decades this galaxy had been classified as an unbarred spiral,
  recent works have unraveled the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}.
  M31 also features a ring-like structure at $R_{\rm maj} \sim 50'$ \citep{athanassoulabeaton2006m31}.

  \emph{1D fit -- }
  We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
  The region $2000'' \lesssim R_{\rm maj} \lesssim 3400''$, where the pseudo-ring is observed, was excluded from the fit.
  A S\'ersic + exponential fit is not adequate to describe the light profile of M31,
  as the residuals of such fit display a structure in correspondence of the bar ($R_{\rm maj} \lesssim 1500''$).
  The addition of a Ferrer function to account for the bar notably improved the fit.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M31.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M31.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-bar & $418.6$  &  $2.2$ \\
  T.W. 1D eq.  & S-bul + e-d + F-bar & $173.6$  &  $1.3$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m31}
  \end{table}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \clearpage\newpage\noindent
  {\bf M49 -- NGC 4472 \\}

  M49, the brightest member of the Virgo cluster, is a giant elliptical galaxy 
  with a slightly resolved partially depleted core \citep{rusli2013}. \\ %($R_{\rm break} = 1''.8$, \citealt{rusli2013}).

  \emph{1D fit -- }
  We excluded from the fit the innermost $12''$.
  We found no evidence for embedded components and
  we fit M49 with a single S\'ersic profile. \\

  \emph{Other models -- } 
  The effective radius estimated by R+13 is larger than that measured by us along the equivalent axis.
  Since their circularized light profile is almost 3 times more extended than ours, 
  it is possible that their best-fit model required a larger $R_{\rm e}$ to account for the galaxy intracluster halo light.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M49.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M49.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c   & $190.2$  &  $6.6$ \\
  T.W. 1D eq.  & S-bul + m-c   & $135.3$  &  $5.4$ \\
  T.W. 2D      & S-bul + m-c   & $151.9$  &  $5.5$ \\
  \hline
  R+13         & core-S\'ersic & $199.0$  &  $5.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m49}
  \end{table}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \clearpage\newpage\noindent
  {\bf M59 -- NGC 4621 \\}

  M59 is an elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
  and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}.\\

  \emph{1D fit -- }
  The intermediate-scale embedded disk is clearly visible in our unsharp mask image, and 
  the velocity field confirms the presence of a rapidly rotating component. 
  This has been modeled with an exponential function.
  We chose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit. \\

  \emph{Other models -- } 
  We observed no significant discrepancies between our results and the best-fit models of S+11 and V+12.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M59.}
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M59.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-n + e-id & $48.0$  &  $5.5$ \\
  T.W. 1D eq.  & S-bul + m-n + e-id & $90.9$  &  $8.8$ \\
  %T.W. 2D	&    & $$  &  $$ \\
  \hline 
  S+11         & S-bul       & $70.1$  &  $5.0$ \\
  V+12         & S-bul + m-c & $54.7$  &  $5.7$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m59}
  \end{table}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%\clearpage\newpage\noindent
  %%
  %%{\bf M60 -- NGC 4649 \\}
  %%
  %%exclude it, doesn't make sense
  %%
  %%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \clearpage\newpage\noindent
  {\bf M64 -- NGC 4826 \\}

  M64 is a dusty spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}. \\

  \emph{1D fit -- }
  A large-scale bar ($R_{\rm maj} \lesssim 50''$) can be identified in the unsharp mask 
  and produces corresponding peaks in the ellipticity, PA and B4 profiles.
  We modeled it with a Ferrer function.
  Additional peaks in the ellipticity, PA and B4 profiles at $R_{\rm maj} \sim 15''$ 
  signal the presence of an embedded disky component, that we described with a low-$n$
  S\'ersic function.
  Although the galaxy is dusty and hosts an AGN, we do not observe any nuclear excess of light 
  in the fit residuals and therefore we consider unnecessary to add a nuclear component to our model. \\

  \emph{Other models -- } 
  The best-fit model of B+12 is in reasonable agreement with our results.

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m64_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for M64.}
  \end{center}
  \end{figure}
